On a quotient topology of the partition lattice with forbidden block sizes

### 2020-08-28 paper2/paper.tex
paper2 small fix

Via the map in the proof of Lemma \ref{trispiso} we obtain the unique simplex $\sigma_{n,k}$ of dimension $l$ with the vertices $v_0\oplus 1^{n-v_0}$ with $v_0=2,\dots,n-1$ and $v_0\equiv 0,1\mod k$, such that $\{[\delta_{\sigma_{n,k}}]\}$ is a basis of the free group $H^l(\Delta_{n,k})$. $[\delta_{\sigma_{n,k}}]$ denotes the class of $\delta_{\sigma_{n,k}}$.
\begin{prop}
The set $\{[\rho_{n,k}]\}$ is a basis of the free group $H^l(\Delta(\Pi_{n,k})/S_1\times S_{n-1})$.
\end{prop}
\begin{proof}
By Lemma \ref{cocycle}, $\rho_{n,k}$ is a cocycle. The homomorphism $\rho_{n,k}$ is not a coboundary by the following argument: Assume there exists $g\in C^{l-1}$ with $\rho_{n,k}=\partial^*g$. If we restrict $\rho_{n,k}$ to $\Delta_{n,k}$, this implies $\sigma_{n,k}=\partial^*\widetilde g$, where $\widetilde g$ is the restriction of $g$ to $\Delta_{n,k}$. It remains to show that $\rho_{n,k}$ is a generator. Assume there exists $f\in\hom(C_l,\Z)$ such that $[\rho_{n,k}]=k[f]$ with $k>1$. Again we restrict to $\Delta_{n,k}$ and obtain $[\sigma_{n,k}]=k[\widetilde f]$. By the discussion above this is a contradiction.
\end{proof}
\bibliographystyle{model1-num-names}
\begin{thebibliography}{00}
\bibitem{bjoern}
A. Bj\"orner, \textit{Matroid Applications}, Cambridge University Press, 1992.
\bibitem{donau}
R. Donau, \textit{Quotients of the order complex $\Delta(\overline{\Pi}_n)$ by subgroups of the Young subgroup $S_1\times S_{n-1}$}, Topology and its Applications \textbf{157} (16) (2010), pp. 2476-2479.
\bibitem{forman}
R. Forman, \textit{Morse theory for cell complexes}, Adv. Math. \textbf{134} (1) (1998), pp. 90-145.
\bibitem{hatcher}
A. Hatcher, \textit{Algebraic Topology}, Cambridge University Press, 2008.
\bibitem{clmap}
D.N. Kozlov, \textit{Closure maps on regular trisps}, Topology and its Applications \textbf{156} (15) (2009), pp. 2491-2495.
\bibitem{kozthm}
D.N. Kozlov, \textit{Collapsibility of $\Delta(\Pi_n)/S_n$ and some related CW complexes}, Proc. Amer. Math. Soc. \textbf{128} (8) (2000), pp. 2253-2259.
\bibitem{buch}
D.N. Kozlov, \textit{Combinatorial Algebraic Topology}, Algorithms and Computation in Mathematics \textbf{21}, Springer-Verlag Berlin Heidelberg, 2008.
\end{thebibliography}
\end{document}

>>>>

Via the map in the proof of Lemma \ref{trispiso} we obtain the unique simplex $\sigma_{n,k}$ of dimension $l$ with the vertices $v_0\oplus 1^{n-v_0}$ with $v_0=2,\dots,n-1$ and $v_0\equiv 0,1\mod k$, such that $\{[\delta_{\sigma_{n,k}}]\}$ is a basis of the free group $H^l(\Delta_{n,k})$. $[\delta_{\sigma_{n,k}}]$ denotes the class of $\delta_{\sigma_{n,k}}$.
\begin{prop}
The set $\{[\rho_{n,k}]\}$ is a basis of the free group $H^l(\Delta(\Pi_{n,k})/S_1\times S_{n-1})$.
\end{prop}
\begin{proof}
By Lemma \ref{cocycle}, $\rho_{n,k}$ is a cocycle. The homomorphism $\rho_{n,k}$ is not a coboundary by the following argument: Assume there exists $g\in C^{l-1}$ with $\rho_{n,k}=\partial^*g$. If we restrict $\rho_{n,k}$ to $\Delta_{n,k}$, this implies $\delta_{\sigma_{n,k}}=\partial^*\widetilde g$, where $\widetilde g$ is the restriction of $g$ to $\Delta_{n,k}$. It remains to show that $\rho_{n,k}$ is a generator. Assume there exists $f\in\hom(C_l,\Z)$ such that $[\rho_{n,k}]=k[f]$ with $k>1$. Again we restrict to $\Delta_{n,k}$ and obtain $[\delta_{\sigma_{n,k}}]=k[\widetilde f]$. By the discussion above this is a contradiction.
\end{proof}
\bibliographystyle{model1-num-names}
\begin{thebibliography}{00}
\bibitem{bjoern}
A. Bj\"orner, \textit{Matroid Applications}, Cambridge University Press, 1992.
\bibitem{donau}
R. Donau, \textit{Quotients of the order complex $\Delta(\overline{\Pi}_n)$ by subgroups of the Young subgroup $S_1\times S_{n-1}$}, Topology and its Applications \textbf{157} (16) (2010), pp. 2476-2479.
\bibitem{forman}
R. Forman, \textit{Morse theory for cell complexes}, Adv. Math. \textbf{134} (1) (1998), pp. 90-145.
\bibitem{hatcher}
A. Hatcher, \textit{Algebraic Topology}, Cambridge University Press, 2008.
\bibitem{clmap}
D.N. Kozlov, \textit{Closure maps on regular trisps}, Topology and its Applications \textbf{156} (15) (2009), pp. 2491-2495.
\bibitem{kozthm}
D.N. Kozlov, \textit{Collapsibility of $\Delta(\Pi_n)/S_n$ and some related CW complexes}, Proc. Amer. Math. Soc. \textbf{128} (8) (2000), pp. 2253-2259.
\bibitem{buch}
D.N. Kozlov, \textit{Combinatorial Algebraic Topology}, Algorithms and Computation in Mathematics \textbf{21}, Springer-Verlag Berlin Heidelberg, 2008.
\end{thebibliography}
\end{document}
